Draft-assinment1

### 2017-02-21 Draft-xuezhou-sjb.Rmd
Add the second paragraph of intro part..

These data are collected by United States Department of Education with the goal of helping students and families make more educated decisions about college and compare vital information easily.

>>>>

The data is collected by United States Department of Education, which corresponds to all undergraduate degree-granting institutions of higher education from 1996 through 2016. The dataset is pretty rich and covers a wide range of topics. It has 1743 associated columns. Each corresponds to one named data variable. All data variables are divided into 10 categories ranging from ‘Root’ category to ‘Earnings’ category. The data type contains integer, string and float. Data elements with an ‘IPEDS’ value in the ‘Source’ field are derived directly from the Integrated Postsecondary Education Data System (IPEDS). For further detailed description of the dataset, you can find it in the CollegeScorecardDataDictionary.xlsx excel file.
